---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![CC BY-NC-SA 4.0][cc-by-nc-sa-shield]][cc-by-nc-sa]

[cc-by-nc-sa]: http://creativecommons.org/licenses/by-nc-sa/4.0/
[cc-by-nc-sa-image]: https://licensebuttons.net/l/by-nc-sa/4.0/88x31.png
[cc-by-nc-sa-shield]: https://img.shields.io/badge/License-CC%20BY--NC--SA%204.0-lightgrey.svg
<!-- badges: end -->

# charts

```{r child = '_intro.Rmd'}
```

# List of charts

- [challengerOrings](#challengerOrings)
- [climateChangeBarcode](#climateChangeBarcode)
- [electionMargins](#electionMargins)
- [electricityEIA](#electricityEIA)
- [ggxaringan](#ggxaringan)
- [lcetPatenting](#lcetPatenting)
- [newEnergyInvestment](#newEnergyInvestment)
- [scienceCommentary2019](#scienceCommentary2019)
- [scotusNominations](#scotusNominations)
- [solarPvProduction](#solarPvProduction)
- [usHighwayFund](#usHighwayFund)
- [usPevSales](#usPevSales)
- [usSolarIndustry](#usSolarIndustry)
- [worldNuclearAssociation](#worldNuclearAssociation)

```{r child = '_description.Rmd'}
```

-----

## Author and License Information

- Author: *John Paul Helveston* https://www.jhelvy.com/
- This work is licensed under a
[Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License][cc-by-nc-sa].

[![CC BY-NC-SA 4.0][cc-by-nc-sa-image]][cc-by-nc-sa]
